---
title: "Project1final.rmd"
output: html_document
---

```{r}
library(DT)
library(MASS)
library(car)
```


```{r}
HP<- read.table("http://ww2.amstat.org/publications/jse/datasets/homes76.dat.txt",header=TRUE)
```

```{r}
HP<-HP[-c(1,7,10,15,16,17,18,19)]
```

```{r}
names(HP)[names(HP) == 'Y'] <- 'price'
names(HP)[names(HP) == 'X1'] <- 'size'
names(HP)[names(HP) == 'X2'] <- 'lot'
names(HP)[names(HP) == 'X3'] <- 'bath'
names(HP)[names(HP) == 'X4'] <- 'bed'
names(HP)[names(HP) == 'X5'] <- 'age'
names(HP)[names(HP) == 'X6'] <- 'garage'
names(HP)[names(HP) == 'D7'] <- 'active'
```

```{r}
datatable(HP)
```

```{r}
mean(HP$size)
mean(HP$lot)
mean(HP$year)
```

## Using stepAIC

price is measured in hundreds of thousands of dollars and size is measured in thousands of square feet. 

```{r}
 full<-lm(price~.,data=HP)
```

```{r}
mod.be<-stepAIC(full,direction =c ("backward"))
```

```{r}
back<-lm(price~1,data=HP)
```

```{r}
mod.fs<-stepAIC(back, scope =list (upper=full,lower=back ))
```

I believe mod.be is better because it gives us more variables that are statiscally significant

## mod1

```{r}
mod1<-lm(price~ size + lot + bath + bed + age + garage + active + elem, data=HP)

summary(mod1)

residualPlots(mod1)
```

It looks like a quadratic function is fitting to most of my plots instaed of a linear function, so it seems that I would need to square some of the variables

The Adjusted $R^2 = .4411$

## mod2

```{r}
mod2<-lm(price~ size + lot + bath + bath:bed + bed + age + I(age^2) + garage + active + elem, data=HP)

summary(mod2)
```

The Adjusted $R^2 = .4686$

## mod3

```{r}
mod3<-lm(price~ size + lot + bath + bath:bed + bed + age + I(age^2) + garage + active + I(elem == 'edison') + I(elem == 'harris'), data=HP)

summary(mod3)
```

##  training mean square prediction error f

```{r}
mean(resid(mod.fs)^2)
```

```{r}
mean(resid(mod.be)^2)
```

```{r}
mean(resid(mod1)^2)
```

```{r}
mean(resid(mod2)^2)
```

```{r}
mean(resid(mod3)^2)
```

mod2 has the smallest training mean square prediction error. Yes I do thik it will have the smallest test mean square prediction error

## mod 3 prediction interval

```{r}
newdata<-data.frame(size=1.879,lot=4, bath=2.5, bed=3, year=1975, garage=2, age =.5, elem = "Parker", active = 1)

predict(mod3,newdata,interval="predict")
```

